Predictors of frog survival following translocations - supplemental analyses

### 2023-02-21 code/translocation_survival_analysis_suppl.Rmd
Revise axis labels of bd load figure

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    facet_grid(. ~ site_id1) +
    theme(axis.text.x = element_text(angle = 90))
```

>>>>

d1 %>% 
  mutate(period = factor(period, levels = c("before", "after"))) %>% 
  ggplot(aes(x = period, y = log10(bd_load + 1))) +
    geom_boxplot() + 
    labs(x = "Period", y = "Bd load (log10(bd_load + 1))") +
    facet_grid(. ~ site_id1) +
    theme(axis.text.x = element_text(angle = 90))
ggsave(here::here("doc", "manuscript", "figures", "bdload_beforeafter.png"), width = 5, height = 3)
```
